---
title: "UBD Beamer Theme using R Markdown"
subtitle: "An example presentation document with R code"
author: "Haziq Jamil"
institute: |
  | Mathematical Sciences, Faculty of Science, UBD
  | \url{https://haziqj.ml}
output: 
  beamer_presentation:
    template: ubd_beamer_rmd.tex
    latex_engine: xelatex
    slide_level: 3
    keep_tex: true
toc: true
toctitle: "Overview"
banner: true
logo: true
progressdots: false
handout: false
bibliography: refs.bib
---

```{r setup, include=FALSE}
# options(tinytex.bib_engine = "biber")
knitr::opts_chunk$set(echo = FALSE, tidy.opts = list(width.cutoff = 50),
                      tidy = TRUE)
```

# Introduction

### Introduction

The UBD Beamer Theme is a modern and minimal theme designed for getting information across in a clean and uncluttered manner.
	
This theme is based on the [Saarland Beamer Theme](https://github.com/kailashbuki/beamerthemesaarland), with its logos and fonts changed, and colour scheme adapted to UBD's pastel-ised colour scheme.

# Features

## Lists

### Slide full of lists

*Universiti Brunei Darussalam* (UBD; translation University of Brunei Darussalam; Jawi: \textarabic{يونيبرسيتي بروني دارالسلام}) is the first university in Brunei.

- UBD in figures
  - **Established**: 1985
  - **Medium of instruction**: English
  - **Academic faculties**: 9
  - **Research Institutes**: 7
  - **Student enrolment**: 3,137 (in 2015, approx.)
- History
  - **1985**: UBD established, first campus in Gadong
  - **1995**: UBD moved to Tungku Link
  - **2009**: Introduction of [GenNEXT Programme](https://ubd.edu.bn/admission/undergraduate/gennext-degree-programme/)
  - **2011**: Commencement of the first Discovery Year programme		
- Credits: \url{https://ubd.edu.bn/} and Wikipedia

## Blocks

### Blocks

::: {.block}
#### Standard Block
This is a standard block using the \texttt{block} environment.
:::

\begin{exampleblock}{Example Block}
	This is an example block using the \texttt{exampleblock} environment.
\end{exampleblock}

\begin{alertblock}{Alert Block}
	This is an alert block using the \texttt{alertblock} environment.
\end{alertblock}

## Quotes

### Quotation

> Archimedes will be remembered when Aeschylus is forgotten, because languages die and mathematical ideas do not. ``Immortality'' may be a silly word, but probably a mathematician has the best chance of whatever it may mean.

\hfill --- G. H. Hardy in *A Mathematician's Apology, 1941*

## Columns

### Two columns

We can also add two columns in the slides.
		\begin{columns}[t]
			\begin{column}[T]{0.4\textwidth}
				This is the first column. In this column, we can also add a block for instance.
				\vspace{1em}
				\begin{block}{Block}
					I am a block in a column.
				\end{block}
			\end{column}
			\begin{column}[T]{0.4\textwidth}
				\begin{itemize}
					\item In this column,
					\item we just add the
					\item bullet points.
				\end{itemize}
			\end{column}
		\end{columns}

## Colour palette

### Colour palette

- \color{navyblue} Frame titles: \texttt{navyblue}
- \color{gray} Structure: \texttt{gray}
- \color{charcoal} Standard block: \texttt{charcoal}
- \color{solidpink} Alerted block: \texttt{solidpink}
- \color{queenpink} Alerted block bg: \texttt{queenpink}
- \color{myrtlegreen} Example block: \texttt{myrtlegreen}
- \color{lightcyan} Example block: \texttt{lightcyan}
- \color{orangecrayola} Misc 1: \texttt{orangecrayola}
- \color{paradisepink} Misc 2: \texttt{paradisepink}

## Mathematics

### Mathematics

Let $X\sim\mathrm{Pois}(\lambda)$. 
The probability mass function of $X$ is given by
\begin{align}\label{eq:pois}
	\Pr(X=x) = \frac{e^{-\lambda}\lambda^x}{x!}.
\end{align}
Using the pmf given in \eqref{eq:pois}, we can derive the moment generating function for $X$ to be:
\begin{align*}
	M_X(t) 
	&= \sum_{k=0}^\infty e^{tx} \cdot \frac{e^{-\lambda}\lambda^x}{x!} \\
	&= e^{-\lambda} \sum_{k=0}^\infty  \frac{(\lambda e^t)^x}{x!} \\
	&= e^{-\lambda}  e^{\lambda e^t} \\
	&= \exp\{\lambda(e^t - 1) \}.
\end{align*}

### Theorems et al.

\begin{definition}[Prime numbers]
	A prime number is a natural number greater than 1 that is not a product of two smaller natural numbers.
\end{definition}

\begin{theorem}[Infinitude of primes]
	There are an infinite number of prime numbers.
\end{theorem}

\begin{proof}
	Suppose that there exist only a finite number of primes, $p_1,\dots,p_n$, say.
	The number 
	\[
	  N = 1+p_1\cdots p_n
	\]
	is divisible by some prime $p$.
	But $p$ cannot be any of $p_1,\dots,p_n$, since the latter all leave remainder 1 on dividing $N$.
	This contradicts our assumption that $p_1,\dots,p_n$ is the complete list of primes.
\end{proof}

### A maths example

Maths examples are continuously numbered (using the \texttt{example} environment).
	
\begin{example}[Examples of prime numbers]
	2, 3, 5, 7 and 11 are examples of prime numbers.
\end{example}

\begin{example}[Examples of non-prime numbers]
	Since $4 = 2 \times 2$, it is not a prime.
\end{example}

# Citations

### Citations

The importance of grounding one's self in elementary probability theory and mathematical statistics cannot be overstated.
Here are some excellent fundamental textbooks every student of statistics should read: @casella2002statistical, @pawitan2001all, and @wasserman2013all.

\blfootnote{It is highly suggested to use pandoc's way of generating bibliographies (see \href{https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html}{here}) rather than using Biblatex. This footnote was created using the custom \texttt{\textbackslash blfootnote\{\}} command.}

<!-- The importance of grounding one's self in elementary probability theory and mathematical statistics cannot be overstated. -->
<!-- 	Here are some excellent fundamental textbooks every student of statistics should read: \citet{casella2002statistical,	pawitan2001all, wasserman2013all}. \\[1em] -->

<!-- \begin{alertblock}{Warning} -->
<!-- 		Using fancy tools like neural nets, boosting, and support vector machines without understanding basic statistics is like doing brain surgery before knowing how to use a band-aid \citep{wasserman2013all}. -->
<!-- \end{alertblock} -->

# Using `R`

### Syntax highlighting

```{r rcode, echo = TRUE, eval = FALSE}
# function args are keywords c; function names are keywords d
foo = function(arg1 = 100, arg2 = "character string") {
  if (TRUE) {
    x = NULL  # if, function, NULL are keywords a
    for (i in 1:10) x = c(x, mean(3 * rnorm(100) + 1))
  }
}

# <-, = and -> are keywords b
x <- TRUE && FALSE %in% c(T, F)
```

### Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

### Slide with Plot

```{r pressure}
plot(pressure)
```

# Conclusion

### Conclusion

To use this theme, download the `ubd_beamer_rmd.tex` file, `.sty` files, and image files (for the logo and banner) from \url{https://github.com/haziqj/ubd-beamer}, and place the files together with your `.Rmd` source file. Use the sample `slides_rmd.Rmd` as a guide.

### End

\centering
\Huge Thank you!

### References
