---
title: UBD Beamer Theme using RMarkdown
subtitle: An example presentation document with R code
author: Haziq Jamil
institute: |
  | Mathematical Sciences, Faculty of Science, UBD
  | \url{https://haziqj.ml}
output: 
  beamer_presentation:
    template: ubd_beamer_rmd.tex
    latex_engine: xelatex
    slide_level: 3
    keep_tex: true
    citation_package: biblatex
    pandoc_args: ["--lua-filter=luafilters/mycustom.lua", "--lua-filter=luafilters/bookdown.lua"] 
aspectratio: 43
toc: true
toctitle: "Overview"
tocmulticol: 
banner: true
logo: true
progressdots: false
handout: false
bibliography: refs.bib
refslide: true
thankyou: true
# header-includes:
#   - \usepackage{lipsum}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.height = 4, fig.width = 6, 
                      cache = TRUE, warning = FALSE, message = FALSE,
                      fig.path = "figure/", cache.path = "_cache/",
                      fig.align = "center")
options(width = 55)  # if 4:3 set to 55, otherwise 70
library(tidyverse)
theme_set(theme_classic())
```

# Introduction

The UBD Beamer Theme is a modern and minimal theme designed for getting information across in a clean and uncluttered manner.
	
This theme is based on the [Saarland Beamer Theme](https://github.com/kailashbuki/beamerthemesaarland), with its logos and fonts changed, and colour scheme adapted to UBD's pastel-ised colour scheme.

# Features

## Lists

### Slide full of lists

*Universiti Brunei Darussalam* (UBD; translation University of Brunei Darussalam; Jawi: \textarabic{يونيبرسيتي بروني دارالسلام}) is the first university in Brunei.

- UBD in figures
  - **Established**: 1985
  - **Medium of instruction**: English
  - **Academic faculties**: 9
  - **Research Institutes**: 7
  - **Student enrolment**: 3,137 (in 2015, approx.)
- History
  - **1985**: UBD established, first campus in Gadong
  - **1995**: UBD moved to Tungku Link
  - **2009**: Introduction of [GenNEXT Programme](https://ubd.edu.bn/admission/undergraduate/gennext-degree-programme/)
  - **2011**: Commencement of the first Discovery Year programme		
- Credits: \url{https://ubd.edu.bn/} and Wikipedia

## Blocks

::: {.block}
#### Standard Block
This is a standard block using the `block` environment.
:::

::: {.exampleblock latex="{Example Block}"}
This is an example block using the `exampleblock` environment.
:::

::: {.alertblock latex="{Alert Block}"}
This is an alert block using the `alertblock` environment.
:::

::: {.altblock latex="{Alternative Block}"}
This is an alternatively-coloured block using the `altblock` environment.
:::


## Quotes

### Quotation

> Archimedes will be remembered when Aeschylus is forgotten, because languages die and mathematical ideas do not. "Immortality" may be a silly word, but probably a mathematician has the best chance of whatever it may mean.

\hfill --- G. H. Hardy in *A Mathematician's Apology, 1941*

## Columns

### Two columns

We can also add two columns in the slides.

\vspace{1em}

::::: {.columns}

:::: {.column width=48%}

This is the first column. 
In this column, we can also add a block for instance.

::: {.block}
#### Block
I am a block in a column.
:::


::::

:::: {.column width=48%}

- In this column,
- we just add the
- bullet points.

::::

:::::

## Colour palette

- [Blues: `ubdblue` a.k.a. Dark Cornflower Blue (#325494)]{color=ubdblue}
- [Teals: `ubdteal` a.k.a. Upsdell Red (#B10F2E)]{color=ubdteal}
- [Yellows: `ubdyellow` a.k.a. Maize Crayola Red (#F5C946)]{color=ubdyellow}
- [Alerted text: `ubdred` a.k.a. Upsdell Red (#B10F2E)]{color=ubdred}
- [Normal text: `ubdblack` a.k.a. Dark Sienna (#230C0F)]{color=ubdblack}
- [Grays: `gray` a.k.a. Spanish Gray (#999999)]{color=gray}
<!-- - [Frame background: `ubdblue` (#325494)]{color=ubdblue} -->
<!-- - [Example block: `ubdteal` a.k.a. Upsdell Red (#B10F2E)]{color=ubdred} -->




<!-- - \color{navyblue} Frame titles: \texttt{navyblue} -->
<!-- - \color{gray} Structure: \texttt{gray} -->
<!-- - \color{charcoal} Standard block: \texttt{charcoal} -->
<!-- - \color{solidpink} Alerted block: \texttt{solidpink} -->
<!-- - \color{queenpink} Alerted block bg: \texttt{queenpink} -->
<!-- - \color{myrtlegreen} Example block: \texttt{myrtlegreen} -->
<!-- - \color{lightcyan} Example block: \texttt{lightcyan} -->
<!-- - \color{orangecrayola} Misc 1: \texttt{orangecrayola} -->
<!-- - \color{paradisepink} Misc 2: \texttt{paradisepink} -->

## Mathematics

### Mathematics

Let $X\sim\operatorname{Pois}(\lambda)$. 
The probability mass function of $X$ is given by
\begin{align}\label{eq:pois}
	\Pr(X=x) = \frac{e^{-\lambda}\lambda^x}{x!}.
\end{align}
Using the pmf given in \eqref{eq:pois}, we can derive the moment generating function for $X$ to be:
\begin{align*}
	M_X(t) 
	&= \sum_{k=0}^\infty e^{tx} \cdot \frac{e^{-\lambda}\lambda^x}{x!} \\
	&= e^{-\lambda} \sum_{k=0}^\infty  \frac{(\lambda e^t)^x}{x!} \\
	&= e^{-\lambda}  e^{\lambda e^t} \\
	&= \exp\{\lambda(e^t - 1) \}.
\end{align*}

### Theorems et al.

::: {.definition name="Prime numbers"}
A prime number is a natural number greater than 1 that is not a product of two smaller natural numbers.
:::

::: {.theorem name="Infinitude of primes"}
There are an infinite number of prime numbers.
:::

::: {.proof}
Suppose that there exist only a finite number of primes, $p_1,\dots,p_n$, say.
The number 
$$
N = 1+p_1\cdots p_n
$$
is divisible by some prime $p$.
But $p$ cannot be any of $p_1,\dots,p_n$, since the latter all leave remainder 1 on dividing $N$.
This contradicts our assumption that $p_1,\dots,p_n$ is the complete list of primes.

:::

### A maths example

Maths examples are continuously numbered (using the \texttt{example} environment).
	
::: {.example name="Examples of prime numbers"}
2, 3, 5, 7 and 11 are examples of prime numbers.
:::
	
::: {.example name="Examples of non-prime numbers"}
Since $4 = 2 \times 2$, it is not a prime.
:::

## Citations

The importance of grounding one's self in elementary probability theory and mathematical statistics cannot be overstated.
Here are some excellent fundamental textbooks every student of statistics should read: @casella2002statistical, @pawitan2001all, and @wasserman2013all.

\blfootnote{It is highly suggested to use pandoc's way of generating bibliographies (see \href{https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html}{here}) rather than using Biblatex. This footnote was created using the custom \texttt{\textbackslash blfootnote\{\}} command.}

<!-- The importance of grounding one's self in elementary probability theory and mathematical statistics cannot be overstated. -->
<!-- 	Here are some excellent fundamental textbooks every student of statistics should read: \citet{casella2002statistical,	pawitan2001all, wasserman2013all}. \\[1em] -->

<!-- \begin{alertblock}{Warning} -->
<!-- 		Using fancy tools like neural nets, boosting, and support vector machines without understanding basic statistics is like doing brain surgery before knowing how to use a band-aid \citep{wasserman2013all}. -->
<!-- \end{alertblock} -->

## Using `R`

### Syntax highlighting

```{r rcode, echo = TRUE, eval = FALSE}
f <- function(x) {
  # Check small prime
  if (x > 10 || x < -10) {
    stop("Input too big")
  } else if (x %in% c(2, 3, 5, 7)) {
    cat("Input is prime!\n")
  } else if (x %% 2 == 0) {
    cat("Input is even!\n")
  } else if (x %% 2 == 1) {
    cat("Input is odd!\n")
  }
}
```

### Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

### Slide with Plot

```{r pressure, echo = TRUE, fig.height = 3}
ggplot(tibble(x = rnorm(100), y = rnorm(100)), aes(x, y)) +
  geom_point()
```

# Conclusion

### Conclusion

To use this theme, download the `ubd_beamer_rmd.tex` file, `.sty` files, and image files (for the logo and banner) from \url{https://github.com/haziqj/ubd-beamer}, and place the files together with your `.Rmd` source file. Use the sample `slides_rmd.Rmd` as a guide.
