---
title: UBD Beamer Theme using RMarkdown
subtitle: An example presentation document with R code
author: Haziq Jamil
institute: |
  | Mathematical Sciences, Faculty of Science, UBD
  | \url{https://haziqj.ml}
date: 
output: 
  beamer_presentation:
    template: ubd_beamer_rmd.tex
    latex_engine: xelatex
    slide_level: 3
    keep_tex: true
    citation_package: biblatex
    pandoc_args: ["--lua-filter=luafilters/mycustom.lua", "--lua-filter=luafilters/bookdown.lua"] 
aspectratio: 43
handout: false
toc: true
toctitle: Overview
tocmulticol: 
transitions: false
progressdots: false
bibliography: refs.bib
bibstyle: authoryear
refslide: false
thankyou: false
header-includes:
  - \usepackage{lipsum}
  - \SetLipsumLanguage{english}
include-after:
  - \backupend
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE,
  message = FALSE,
  fig.height = 4, 
  fig.width = 6, 
  fig.path = "figure/", 
  fig.align = "center",
  cache = TRUE, 
  cache.path = "_cache/"
)
options(width = 55)  # if 4:3 set to 55, otherwise 70
library(tidyverse)
theme_set(theme_classic())
```

# Introduction

The UBD Beamer Theme is a modern and minimal theme designed for getting information across in a clean and uncluttered manner. \bigskip

This theme is based on the [Saarland Beamer Theme](https://github.com/kailashbuki/beamerthemesaarland), with its logos and fonts changed, and colour scheme adapted to UBD's official brand colours.

# Features

## Lists

### Slide full of lists

*Universiti Brunei Darussalam* (UBD; translation University of Brunei Darussalam; Jawi: \textarabic{يونيبرسيتي بروني دارالسلام}) is the first university in Brunei.

- UBD in figures
  - **Established**: 1985
  - **Medium of instruction**: English
  - **Academic faculties**: 9
  - **Research Institutes**: 7
  - **Student enrolment**: 3,137 (in 2015, approx.)
- History
  - **1985**: UBD established, first campus in Gadong
  - **1995**: UBD moved to Tungku Link
  - **2009**: Introduction of [GenNEXT Programme](https://ubd.edu.bn/admission/undergraduate/gennext-degree-programme/)
  - **2011**: Commencement of the first Discovery Year programme		
- Credits: \url{https://ubd.edu.bn/} and Wikipedia

## Blocks

::: {.block}
#### Standard Block
This is a standard block using the `block` environment.
:::

::: {.exampleblock latex="{Example Block}"}
This is an example block using the `exampleblock` environment.
:::

::: {.alertblock latex="{Alert Block}"}
This is an alert block using the `alertblock` environment.
:::

::: {.altblock latex="{Alternative Block}"}
This is an alternatively-coloured block using the `altblock` environment.
:::


## Quotes

### Quotation

> Archimedes will be remembered when Aeschylus is forgotten, because languages die and mathematical ideas do not. "Immortality" may be a silly word, but probably a mathematician has the best chance of whatever it may mean.

\hfill --- G. H. Hardy in *A Mathematician's Apology, 1941*

## Columns

### Two columns

We can also add two columns in the slides.\bigskip

::::: {.columns}

:::: {.column width=48%}

This is the first column. 
In this column, we can also add a block for instance.

::: {.block}
#### Block
I am a block in a column.
:::


::::

:::: {.column width=48%}

- In this column,
- we just add the
- bullet points.

::::

:::::

## Colour palette

- [Blues: `ubdblue` a.k.a. Y In Mn Blue (#325494)]{color=ubdblue}
- [Teals: `ubdteal` a.k.a. Medium Aquamarine (#58DDB3)]{color=ubdteal}
- [Yellows: `ubdyellow` a.k.a. Maize Crayola Red (#F5C946)]{color=ubdyellow}
- [Alerted text: `ubdred` a.k.a. Upsdell Red (#B10F2E)]{color=ubdred}
- [Normal text: `ubdblack` a.k.a. Dark Sienna (#230C0F)]{color=ubdblack}
- [Grays: `gray` a.k.a. Spanish Gray (#999999)]{color=gray}

[https://coolors.co/palette/325494-58ddb3-f5c946-b10f2e-230c0f]{.blfootnote}

### Fonts

The font is left to the default beamer font (which I believe is the Computer Modern).
In order to get the sans-serif fonts for the mathematics (including the greek letters), the following lines are called in the `.sty` file:

```latex
\usepackage{cmbright}
\usefonttheme{professionalfonts}
```

So compiling using pdf\LaTeX\ should get the desired output. \medskip

On the other hand, compiling with Xe\LaTeX\ seems to mess up the fonts, probably because legacy fonts are loaded.
There is a switch in the `.sty` file which loads `fontspec` package to fix this (kind of?).

## Mathematics

Let $X$ be a simple random variable defined on $(\Omega,\mathcal F,\mathbb P)$ that takes on finitely many values $\{x_1,\dots,x_n\}$.
The expectation of $X$, $\operatorname{E}(X)$, is the Lebesgue integral of $X$ with respect to $\mathbb P$,
$$
\operatorname{E}(X) := \int X(\omega) \operatorname{d \mathbb P} = \sum_{i=1}^n x_i \operatorname{\mathbb P}(\omega \in A_i),
$$
where $A_i=\{\omega\in\Omega \mid X(\omega)=x_i \}$.

\vspace{-0.5em}

\begin{gather*}
AaBbCcDdEeFfGgHhIiJjKkLlMmNnOoPpQqRrSsTtUuVv\\WwXxYyZz \\[0.5em]
1234567890 \\[0.5em]
\alpha
 \beta
\Gamma  \gamma
\Delta  \delta
\epsilon  \varepsilon	
\zeta
\eta
\Theta \theta  \vartheta
\iota
\kappa  \varkappa
\Lambda  \lambda
\mu
\nu
\Xi  \xi
\Pi \pi  \varpi
\rho  
\Sigma \sigma 
\tau
\Upsilon  \upsilon
\Phi \phi  \varphi
\chi
\Psi  \psi
\Omega  \omega \\[0.5em]
\prod \oint \bigoplus \bigotimes \bigcup \bigcap 
\end{gather*}

### Theorems et al.

::: {.definition name="Prime numbers"}
A prime number is a natural number greater than 1 that is not a product of two smaller natural numbers.
:::

::: {.theorem name="Infinitude of primes"}
There are an infinite number of prime numbers.
:::

::: {.proof}
Suppose that there exist only a finite number of primes, $p_1,\dots,p_n$, say.
The number 
$$
N = 1+p_1\cdots p_n
$$
is divisible by some prime $p$.
But $p$ cannot be any of $p_1,\dots,p_n$, since the latter all leave remainder 1 on dividing $N$.
This contradicts our assumption that $p_1,\dots,p_n$ is the complete list of primes.
:::

### Example blocks

Example blocks are continuously numbered (using the `example` environment).
	
::: {.example name="Examples of prime numbers"}
The numbers

- 2;
- 3;
- 5; and
- 7

are examples of prime numbers.
:::
	
::: {.example name="Examples of non-prime numbers"}
Since $4 = 2 \times 2$, it is not a prime.
:::

## Citations

The importance of grounding one's self in elementary probability theory and mathematical statistics cannot be overstated.
Here are some excellent fundamental textbooks every student of statistics should read: @casella2002statistical, @pawitan2001all, and @wasserman2013all.

\blfootnote{It is highly suggested to use pandoc's way of generating bibliographies (see \href{https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html}{here}) rather than using Biblatex. This footnote was created using the custom \texttt{\textbackslash blfootnote\{\}} command.}

<!-- The importance of grounding one's self in elementary probability theory and mathematical statistics cannot be overstated. -->
<!-- 	Here are some excellent fundamental textbooks every student of statistics should read: \citet{casella2002statistical,	pawitan2001all, wasserman2013all}. \\[1em] -->

<!-- \begin{alertblock}{Warning} -->
<!-- 		Using fancy tools like neural nets, boosting, and support vector machines without understanding basic statistics is like doing brain surgery before knowing how to use a band-aid \citep{wasserman2013all}. -->
<!-- \end{alertblock} -->

## Using `R`

### Syntax highlighting

```{r rcode, echo = TRUE, eval = FALSE}
f <- function(x) {
  # Check small prime
  if (x > 10 || x < -10) {
    stop("Input too big")
  } else if (x %in% c(2, 3, 5, 7)) {
    cat("Input is prime!\n")
  } else if (x %% 2 == 0) {
    cat("Input is even!\n")
  } else if (x %% 2 == 1) {
    cat("Input is odd!\n")
  }
}
```

### Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

### Slide with Plot

\vspace{-1em}

```{r slideplot, echo = TRUE, fig.height = 3}
ggplot(tibble(x = rnorm(100), y = rnorm(100)), aes(x, y)) +
  geom_point()
```

# Conclusion

To use this theme, download and place the following files and folders into your working directory:

1. `beamerthemeUBD.sty` (the beamer theme)
2. `ubd_beamer_rmd.tex` (the Rmd beamer template)
3. `luafilters/` (the lua filters in the folder)
4. `ubd_brand.pdf` (the university logo)

To start, you may use the `slides_rmd.Rmd` as a guide and edit from there.

::: {.block}
#### For non-Rmd beamer
All you need is 1. and 4. (the Rmd template and lua filters are not necessary). 
See the file `minimal_example.tex`.
:::


### End {.plain .noframenumbering}

\centering
\Huge
[Thank you!]{color=ubdblue}

### References {.t .allowframebreaks .noframenumbering .plain}

\printbibliography[heading=none]

\appendix
\backupbegin

#  Backup slides

Often times in a presentation, we don't have enough time to present everything, but it's a good idea to prepare backup slides in case the audience asks about it afterwards.\bigskip

We can achieve that using the `\appendix` usage.

# Backup topic 1

\lipsum[1]

# Backup topic 2

::: {.block}
#### A block

\lipsum[4]

:::
